### 2017-04-14 paper/oopsla17-submission/discussion.tex
shuffle

\section{Discussion}
\label{sec:discussion}

@@

>>>>

\section{Limitations and Threats to Validity}
\label{sec:discussion}

\subsection{Limitations}
\label{sec:limitations}

@@

\subsection{Threats to Validity}
\label{sec:validity}

Although our experiments demonstrate that our technique can pinpoint type
errors more accurately than the state of the art and that our features are
relevant to blame assignment, our results may not generalize.

One threat to validity associated with supervised machine learning is
overfitting (\ie learning a model that is too complex with respect to
the data).
%
A similar issue that arises in machine learning is model stability (\ie
can small changes to the training set produce large changes in the model?).
%
We mitigate these threats by:
%
(1) using separate training and testing datasets drawn from distinct
student populations (\autoref{sec:quantitative}), demonstrating the
generality of our models; and
%
(2) via cross-validation on the joint dataset
(\autoref{sec:feature-utility}), which demonstrates the stability of our
models by averaging the accuracy of 10 models trained on distinct
subsets of the data.

Our benchmarks were drawn from students in an undergraduate course and
may not be representative of other student populations.
%
We mitigate this threat by including the largest empirical evaluation of
type error localization that we are aware of: over 4,500 pairs of
ill-typed programs and fixes from two instances of the course, with
programs from 102 different students.
%
We acknowledge, of course, that students are not industrial programmers
and our results may not translate to large-scale software development;
however, we are particularly interested in aiding novice programmers
as they learn to work inside the type system.

A related threat to construct validity is our definition of the immedate
next well-typed program as the intended ground truth answer (see
\autoref{sec:overview}, Challenge 2). Students may, in theory, submit
intermediate well-typed program ``rewrites'' between the original ill-typed
program and the final intended answer. Our approach to discarding outliers
(see \autoref{sec:evaluation}) is designed to mitigate this threat.

Our removal of program pairs that changed too much, where our oracle
could not identify the blame of the other tools, or where the other
tools timed out or encountered unsupported language features is another
threat to validity.
%
It is possible that including the programs that changed excessively
would hurt our models, or that the other tools would perform
better on the programs with unsupported language features.
%
We note however that
%
(1) outlier removal is a standard technique in machine learning
\ES{CITE?}; and
%
(2) our Top-1 accuracy margin is large enough that even if we assumed
that \sherrloc were perfect on all of the excluded programs, it would
only tie our \hiddenFH in Top-1 accuracy.
%
\ES{I think this is accurate, but should double check..}

Examining programs written in \ocaml as opposed to \haskell or any other
typed functional language poses yet another threat, common type errors
may differ in different languages.
%
\ocaml is, however, a standard target for research in type error
localization and thus our choice admits a direct comparison with prior
work.
%
Furthermore, the functional core of \ocaml that we support does not
differ significantly from the functional core of \haskell or SML, all of
which are effectively lambda calculi with a Hindley-Milner-style type
system.\footnote{\haskell's type classes are a notable exception, they
  are also known to cause confusing type errors and would be interesting
  to study in future work.}

Finally, our use of student fixes as oracles for the source of type
errors assumes that, on average, students are able to correctly identify
the source of an error.
%
As the students are in the process of learning the language and type
system, this assumption may be faulty.
%
It may be that \emph{expert} users would disagree with many of the
student fixes, and that it is harder to learn a model of expert fixes,
or that the state of the art would be better at predicting expert fixes.
%
As we have noted before, we believe it is reasonable to use student
fixes as oracles because the student is the best judge of what she
\emph{meant} to do.

### 2017-04-14 paper/oopsla17-submission/overview.tex
shuffle

@@

@@

\mypara{Contextual Features: Error Slices}
%
Our contextual features include the
syntactic class of the neighboring
expressions and their inferred types
(when available).
%
However, we have found that
the most important contextual
signal is whether or not the
expression occurs in a
\emph{minimal type error slice}
\citep{Tip2001-qp,Haack2003-vc}
which includes the smallest
subset of all expressions
that are necessary for the
error to manifest.
%
We propose to use type error slices
to communicate to the classifier
which expressions could
\emph{potentially} be blamed --- a
change to an expression outside of
the minimal slice cannot possibly
fix the type error.
%
We empirically demonstrate that
the type error slice is so
important (\autoref{sec:feature-utility})
that it is actually beneficial to
automatically discard expressions
that are not part of the slice,
rather than letting the classifier
learn to do so.
%
Indeed, this domain-specific
insight is crucial for learning
classifiers that significantly
outperform the state-of-the-art.

@@

@@

\mypara{Solution: Rank Locations by ``Confidence''}
%
Fortunately, many machine learning
classifiers produce not only a predicted
label, but also a metric that can be
interpreted as the classifier's
\emph{confidence} in its prediction.
%
Thus, we \emph{rank} each expression
by the classifier's confidence that
it should be blamed, and present only
the top-$k$ predictions to the
user (in practice $k=3$).
%
This use of ranking to report the
results of a program analysis is
popular in other problem domains
\citep[see, \eg][]{Kremenek2003-ck};
we focus explicitly on the use of
data-driven machine learning
confidence as a ranking source.
%
In \autoref{sec:evaluation} we show
that \toolname's ranking approach
yields a high-precision localizer:
when the top-3 locations are considered,
at least one matches an actual student fix
more than 90\% of the time.

>>>>

% \ES{FIXME: this feels a bit redundant with CHALLENGE 1. the main thing i
%  get is that we use student fixes to extract AST-diffs, which is
%  already said in CHALLENGE 1}

@@

%% \ES{FIXME: this feels a bit redundant with CHALLENGE 2. the main things
  %% i get here are that we use sets of feature vectors, and that we can
  %% concatenate vectors to add context. but this is all said in CHALLENGE
  %% 2 already.}

@@

\mypara{Contextual Features: Error Slices}
%
Our contextual features include the
syntactic class of the neighboring
expressions and their inferred types
(when available).
%
However, we have found that
the most important contextual
signal is whether or not the
expression occurs in
a minimal type error slice
\citep{Tip2001-qp,Haack2003-vc}
which includes \emph{a minimal subset}
of all expressions that are
necessary for the error to manifest.
%
(That is, replacing any subterm
with |undefined| or |assert false|
would yield a well-typed program.)
%
We propose to use type error slices
to communicate to the classifier
which expressions could
\emph{potentially} be blamed --- a
change to an expression outside of
the minimal slice cannot possibly
fix the type error.
%
We empirically demonstrate that
the type error slice is so
important (\autoref{sec:feature-utility})
that it is actually beneficial to
automatically discard expressions
that are not part of the slice,
rather than letting the classifier
learn to do so.
%
Indeed, this domain-specific
insight is crucial for learning
classifiers that significantly
outperform the state-of-the-art.

@@

\input{feature-table}

@@

\mypara{Solution: Rank Locations by Confidence}
%
Fortunately, many machine learning
classifiers produce not only a predicted
label, but also a metric that can be
interpreted as the classifier's
\emph{confidence} in its prediction.
%
Thus, we \emph{rank} each expression
by the classifier's confidence that
it should be blamed, and present only
the top-$k$ predictions to the
user (in practice $k=3$).
%
This use of ranking to report the
results of a program analysis is
popular in other problem domains
\citep[see, \eg][]{Kremenek2003-ck};
we focus explicitly on the use of
data-driven machine learning
confidence as a ranking source.
%
In \autoref{sec:evaluation} we show
that \toolname's ranking approach
yields a high-precision localizer:
when the top-3 locations are considered,
at least one matches an actual student fix
more than 90\% of the time.
